---
title: "Sept 27 Pre-Class "
author: "Wei Wang"
output: html_document
---




### Question 1:

Using a loop, print the integers from 1 to 50. 
```{r, echo=TRUE}
for (i in 1:50) {
  print(i)
}
```

### Question 2:

A.  Using a loop, add all the integers between 0 and 1000.
```{r, echo=TRUE}
Sum <-0
for (i in 0:1000){
  Sum <- Sum + i
}

Sum
```

B. Now, add all the EVEN integers between 0 and 1000 (hint: use seq())
```{r, echo=TRUE}
s <- seq(2, 1000, 2)
current.sum <- 0
for (i in s){
  current.sum <- current.sum + i
}
current.sum
```

C. Now, repeat A and B WITHOUT using a loop.
```{r, echo=TRUE}
1000*(1000+1)/2
1000*(1000+2)/4
```
### Question 3:

Here is a dataframe of survey data containing 5 questions :

```{r, echo=TRUE}
survey <- data.frame(
                     "participant" = c(1, 2, 3, 4, 5, 6),
                     "q1" = c(5, 3, 2, 7, 11, 0),
                     "q2" = c(4, 2, 2, 5, -10, 99),
                     "q3" = c(-4, -3, 4, 2, 9, 10),
                     "q4" = c(-30, 5, 2, 23, 4, 2),
                     "q5" = c(88, 4, -20, 2, 4, 2)
                     )
```
The response to each question should be an integer between 1 and 5. Obviously, we have some bad values in the dataframe. The goal of this problem is to fix them.

A. Using a loop, create a new dataframe called survey.clean where all the invalid values (those that are not integers between 1 and 5) are set to NA.
```{r, echo=TRUE}
survey.clean <- survey
for (i in 1:nrow(survey.clean)){
  y <- survey.clean[, i]
  y[(y %in% c(1:5)) == F] <- NA
  survey.clean[, i] <- y
}
survey.clean
```

B. Now, again using a loop, add a new column to the dataframe called "invalid.answers" that indicates, for each participant, how many bad answers they gave.
```{r, echo=TRUE}
survey.clean$invalid.answers <- rep(NA, nrow(survey.clean))
for (i in 1:nrow(survey.clean)){
  y <- survey.clean[i,1:ncol(survey.clean)-1]
  x <- is.na(y)
  survey.clean$invalid.answers[i] <- sum(x)
}
survey.clean
```

